---
title: "Evaluating the Solow Growth Model using the MRW Framework"
author: "Matthew Houser"
output:
  pdf_document: default
  html_document: default
---


```{r, include=FALSE}
#Import packages and data
#install.packages("systemfit")
#install.packages("kableExtra")
#install.packages("DT")
library(xtable)
library(kableExtra)
library(DT)
library(gridExtra)
library(AER)
library(systemfit)
library(knitr)
library(lmtest)
library(readxl)
library(lmtest)
library(tidyverse)
library(dplyr)
library(pastecs)
mrw <- read_csv("mrw.csv")
pwt <- read_excel("pwt91.xlsx", sheet = "Data")
UNdata <- read_csv("UNdata_Export_20190423_172145263/UNdata_Export_20190423_172145263.csv")
WDIData <- read_csv("WDI_csv/WDIData.csv")
```


```{r, echo=FALSE}
#Select only countries used in regression
mrw %>% 
  filter(n==1) -> mrw
#Create list of countries
#mrw csv has a typo in the Congo entry
mrw[10, 2] = "Congo"
countries <- mrw[2]
countries <- unlist(countries)

#Find discrepancsh_ies in naming between datasets, uncomment to view
#setdiff(countries, unlist(WDIData[1]))

#Manually find missing countries and add them to main dataset
#Create dataset of countries to make it easier to search through
test <- unique(WDIData[1])
missingcountries <- c("Central African Republic", "Congo, Rep.", "Egypt, Arab Rep.", "Cote d'Ivoire", "South Africa",  "Congo, Dem. Rep.", "Myanmar", "Hong Kong SAR, China", "Korea, Rep.", "Syrian Arab Republic", "Germany", "Dominican Republic", "Venezuela, RB")

#Add missingcountries to countries
countries <- union(countries, missingcountries)
#Subset WDIdata to only countries in MRW
MRW_WDIData <- WDIData[WDIData$`Country Name` %in% countries,]

#Extract fraction of working age population from population
names(MRW_WDIData)[names(MRW_WDIData) == "Indicator Name"] <- c("Indicator")
MRW_WDIData %>% 
  filter(Indicator ==  "Population ages 15-64 (% of total)") %>% 
  select(c("Country Name", "Country Code", "1960", "1985", "2010"))-> data

names(data) <- c("Country", "countrycode", "1960WAP", "1985WAP", "2010WAP")

#Obtain Secondary school gross enrollment data
MRW_WDIData %>% 
  filter(Indicator == "School enrollment, secondary (% gross)") %>% 
  select("Country Name", 27:33, 52:58) %>% 
  mutate(school85 = coalesce(`1985`, `1984`, `1986`, `1983`, `1987`, `1982`, `1988`)) %>% 
  mutate(school10 = coalesce(`2010`, `2009`, `2011`, `2008`, `2012`, `2007`, `2013`)) %>% 
  select("Country Name", "school85", "school10") -> edu

names(edu) <- c("Country", "GrossEnrollment85", "GrossEnrollment10")

#Merge full data with working age population data
data <- left_join(data, edu, by = "Country")


#Subset PWT data to countries in MRW
countrycodes <- data[2]
#PWT has countrycode for Germany as DEU, while elsewhere it is GER
countrycodes <- unlist(countrycodes)
#Collect PWT data for select years
pwt%>% 
  filter(year == c("1960")) %>% 
  select(c("countrycode", "pop", "cgdpo", "csh_i")) -> pwt60
pwt %>% 
  filter(year == "1985") %>% 
  select(c("countrycode","hc", "pop", "cgdpo", "csh_i")) -> pwt85
pwt %>% 
  filter(year == "2010") %>% 
  select(c("countrycode", "hc", "pop", "cgdpo", "csh_i")) -> pwt10

# Merge datasets together
pwttemp <- left_join(pwt60, pwt85, by = "countrycode")
pwttemp <- left_join(pwttemp, pwt10, by = "countrycode")

#Subset only select countries in MRW
pwtdata <- pwttemp[pwttemp$countrycode %in% countrycodes,]
#Rename columns for convenience
names(pwtdata) <- c("countrycode", "pop60", "cgdpo60", "csh_i60", "hc85", "pop85", "cgdpo85", "csh_i85", "hc10", "pop10", "cgdpo10", "csh_i10")

#merge pwtdata and main data
data <- left_join(data, pwtdata, by = "countrycode")


#Select countries used in MRW from UNdata
 UN <- UNdata[UNdata$`Country or Area` %in% countries,]

#Notice only 89 observations, find missing countries, uncomment to see list  
#setdiff(data$Country, UN$`Country or Area`)
#Search for naming discrepancsh_ies, add names to countries list
missingUNcountries <- c("Bolivia (Plurinational State of)", "Democratic Republic of the Congo", "Congo", "Cô´te d'Ivoire", "Egypt", "China Hong Kong SAR", "Republic of Korea", "United Republic of Tanzania", "United States of America", "Venezuela (Bolivarian Republic of)")
countriesUN <- union(countries, missingUNcountries)
UN <- UNdata[UNdata$`Country or Area` %in% countriesUN,]

names(UN) <- c("Country", "Year", "Variant", "Value")
UN <- spread(UN, Year, Value)

#Rename countries in UNData so they can merge with main dataset
UN[9,1] <- "Bolivia"
UN[24, 1] <- "Congo, Dem. Rep."
UN[22,1] <- "Congo, Rep."
UN[20, 1] <- "Cote d'Ivoire"
UN[28,1] <- "Egypt, Arab Rep."
UN[19,1] <- "Hong Kong SAR, China"
UN[73, 1] <- "Korea, Rep."
UN[93, 1] <- "Tanzania"
UN[94, 1] <- "United States"
UN[96, 1] <- "Venezuela, RB"

UN <- select(UN, -c("Variant"))
names(UN) <- c("Country", "pop1519-85", "pop1519-10")

data <- left_join(data, UN, by = "Country")

#We have all non-oil countries, now add columns for intermediate and OECD
mrw %>% 
  filter(n == "1") %>% 
  select(c("country", "i", "o")) -> mrw

#Capitalize Country
names(mrw) <- c("Country", "i", "O")

#Find discrepancies in country names
#uncomment to see names
#setdiff(data$Country, mrw$Country)

#Rename countries so they can properly merge
mrw[8,1] = "Central African Republic"
mrw[36,1] = "Congo, Dem. Rep."
mrw[10, 1] = "Congo, Rep."
mrw[14, 1] = "Cote d'Ivoire"
mrw[74, 1] = "Dominican Republic"
mrw[11, 1] = "Egypt, Arab Rep."
mrw[60, 1] = "Germany"
mrw[41, 1] = "Hong Kong SAR, China"
mrw[46, 1] = "Korea, Rep."
mrw[40, 1] = "Myanmar"
mrw[30, 1] = "South Africa"
mrw[53, 1] = "Syrian Arab Republic"
mrw[94, 1] = "Venezuela, RB"

#merge columns for Intermediate and OECD countries into the dataset
data <- left_join(data, mrw, by = "Country")
#MRW only select countries for which all data is available for, so exclude here countries that don't have educational data in 2010
data <- data[complete.cases(data),]
```

```{r, include=FALSE}
#Define variables as they will be used in regressions, then select only relevant variables. Repeat this 3 times for data for 
data %>% 
  mutate(WAP60 = (`1960WAP`/100 * pop60) *1000) %>% 
  mutate(WAP85 = (`1985WAP`/100 * pop85) *1000) %>% 
  mutate(WAP10 = (`2010WAP`/100 * pop10) *1000) %>% 
  mutate(s1 = log(100 * (csh_i60 + csh_i85)/2)) %>% 
  mutate(s2 = log(100 * (csh_i85+csh_i10)/2)) %>% 
  mutate(st = log(100 * (csh_i60+csh_i10)/2)) %>% 
  mutate(cgdpo60 = cgdpo60/WAP60) %>% 
  mutate(cgdpo85 = cgdpo85/WAP85) %>% 
  mutate(cgdpo10 = cgdpo10/WAP10) %>% 
  mutate(n1 = ((WAP85 - WAP60)/WAP60)/25) %>% 
  mutate(n2 = ((WAP10 - WAP85)/WAP85)/25) %>% 
  mutate(nt = ((WAP10 - WAP60)/WAP60)/50) %>% 
  mutate(ngd1 = log(n1 + .05)) %>% 
  mutate(ngd2 = log(n2 + .05)) %>% 
  mutate(ngdt = log(nt + .05)) %>% 
  mutate(log60 = log(cgdpo60)) %>% 
  mutate(log85 = log(cgdpo85)) %>% 
  mutate(log10 = log(cgdpo10)) %>% 
  mutate(school85 = log((GrossEnrollment85/100) * (`pop1519-85`/pop85))) %>% 
  mutate(school10 = log((GrossEnrollment10/100) * (`pop1519-10`/pop10))) %>% 
  mutate(sngd1 = s1 - ngd1) %>% 
  mutate(sngd2 = s2 - ngd2) %>% 
  mutate(sngdt = st - ngdt) %>% 
  mutate(schoolngd1 = school85 - ngd1) %>% 
  mutate(schoolngd2 = school10 - ngd2) %>% 
  mutate(schoolngdt = school10 - ngdt) %>% 
  mutate(hc_10 = log(hc10)) %>% 
  mutate(hcngdt = hc_10 - ngdt) %>% 
  select(c(1, 2, 24:47)) -> dfn

data %>% 
  filter(i == 1) %>% 
  mutate(WAP60 = (`1960WAP`/100 * pop60) *1000) %>% 
  mutate(WAP85 = (`1985WAP`/100 * pop85) *1000) %>% 
  mutate(WAP10 = (`2010WAP`/100 * pop10) *1000) %>% 
  mutate(s1 = log(100 * (csh_i60 + csh_i85)/2)) %>% 
  mutate(s2 = log(100 * (csh_i85+csh_i10)/2)) %>% 
  mutate(st = log(100 * (csh_i60+csh_i10)/2)) %>% 
  mutate(cgdpo60 = cgdpo60/WAP60) %>% 
  mutate(cgdpo85 = cgdpo85/WAP85) %>% 
  mutate(cgdpo10 = cgdpo10/WAP10) %>% 
  mutate(n1 = ((WAP85 - WAP60)/WAP60)/25) %>% 
  mutate(n2 = ((WAP10 - WAP85)/WAP85)/25) %>% 
  mutate(nt = ((WAP10 - WAP60)/WAP60)/50) %>% 
  mutate(ngd1 = log(n1 + .05)) %>% 
  mutate(ngd2 = log(n2 + .05)) %>% 
  mutate(ngdt = log(nt + .05)) %>% 
  mutate(log60 = log(cgdpo60)) %>% 
  mutate(log85 = log(cgdpo85)) %>% 
  mutate(log10 = log(cgdpo10)) %>% 
  mutate(school85 = log((GrossEnrollment85/100) * (`pop1519-85`/pop85))) %>% 
  mutate(school10 = log((GrossEnrollment10/100) * (`pop1519-10`/pop10))) %>% 
  mutate(sngd1 = s1 - ngd1) %>% 
  mutate(sngd2 = s2 - ngd2) %>% 
  mutate(sngdt = st - ngdt) %>% 
  mutate(schoolngd1 = school85 - ngd1) %>% 
  mutate(schoolngd2 = school10 - ngd2) %>% 
  mutate(schoolngdt = school10 - ngdt) %>% 
  mutate(hc_10 = log(hc10)) %>% 
  mutate(hcngdt = hc_10 - ngdt) %>% 
  select(c(1, 2, 24:47)) -> dfi
  
data %>% 
  filter(O == 1) %>% 
   mutate(WAP60 = (`1960WAP`/100 * pop60) *1000) %>% 
  mutate(WAP85 = (`1985WAP`/100 * pop85) *1000) %>% 
  mutate(WAP10 = (`2010WAP`/100 * pop10) *1000) %>% 
  mutate(s1 = log(100 * (csh_i60 + csh_i85)/2)) %>% 
  mutate(s2 = log(100 * (csh_i85+csh_i10)/2)) %>% 
  mutate(st = log(100 * (csh_i60+csh_i10)/2)) %>% 
  mutate(cgdpo60 = cgdpo60/WAP60) %>% 
  mutate(cgdpo85 = cgdpo85/WAP85) %>% 
  mutate(cgdpo10 = cgdpo10/WAP10) %>% 
  mutate(n1 = ((WAP85 - WAP60)/WAP60)/25) %>% 
  mutate(n2 = ((WAP10 - WAP85)/WAP85)/25) %>% 
  mutate(nt = ((WAP10 - WAP60)/WAP60)/50) %>% 
  mutate(ngd1 = log(n1 + .05)) %>% 
  mutate(ngd2 = log(n2 + .05)) %>% 
  mutate(ngdt = log(nt + .05)) %>% 
  mutate(log60 = log(cgdpo60)) %>% 
  mutate(log85 = log(cgdpo85)) %>% 
  mutate(log10 = log(cgdpo10)) %>% 
  mutate(school85 = log((GrossEnrollment85/100) * (`pop1519-85`/pop85))) %>% 
  mutate(school10 = log((GrossEnrollment10/100) * (`pop1519-10`/pop10))) %>% 
  mutate(sngd1 = s1 - ngd1) %>% 
  mutate(sngd2 = s2 - ngd2) %>% 
  mutate(sngdt = st - ngdt) %>% 
  mutate(schoolngd1 = school85 - ngd1) %>% 
  mutate(schoolngd2 = school10 - ngd2) %>% 
  mutate(schoolngdt = school10 - ngdt) %>% 
  mutate(hc_10 = log(hc10)) %>% 
  mutate(hcngdt = hc_10 - ngdt) %>% 
  select(c(1, 2, 24:47)) -> dfO

```


```{r, include=FALSE}
#Model suffixes are relevant end year of 25 year period or 50 for 1960-2010, T or A for textbook or augmented model, and n, i or O for non-oil, intermediate or OECD countries
model85Tn <- lm(log85 ~ s1 + ngd1, dfn)
model10Tn <- lm(log10 ~ s2 + ngd2, dfn)
model50Tn <- lm(log10 ~ st + ngdt, dfn)
modeltest85Tn <- lm(log85 ~ sngd1, dfn)
modeltest10Tn <- lm(log10 ~ sngd2, dfn)
modeltest50Tn <- lm(log10 ~ sngdt, dfn)
model85An <- lm(log85 ~ s1 + ngd1 + school85, dfn)
model10An <- lm(log10 ~ s2 + ngd2 + school10, dfn)
model50An <- lm(log10 ~ st + ngdt + school10 , dfn)
modeltest85An <- lm(log85 ~ sngd1 + schoolngd1, dfn)
modeltest10An <- lm(log10 ~ sngd2 + schoolngd2, dfn)
modeltest50An <- lm(log10 ~ sngdt + schoolngdt, dfn)
model85Ti <- lm(log85 ~ s1 + ngd1, dfi)
model10Ti <- lm(log10 ~ s2 + ngd2, dfi)
model85Ai <- lm(log85 ~ s1 + ngd1 + school85, dfi)
model10Ai <- lm(log10 ~ s2 + ngd2 + school10, dfi)
model50Ti <- lm(log10 ~ st + ngdt, dfi)
model50Ai <- lm(log10 ~ st + ngdt + school10 , dfi)
modeltest85Ti <- lm(log85 ~ sngd1, dfi)
modeltest10Ti <- lm(log10 ~ sngd2, dfi)
modeltest50Ti <- lm(log10 ~ sngdt, dfi)
modeltest85Ai <- lm(log85 ~ sngd1 + schoolngd1, dfi)
modeltest10Ai <- lm(log10 ~ sngd2 + schoolngd2, dfi)
modeltest50Ai <- lm(log10 ~ sngdt + schoolngdt, dfi)
model85To <- lm(log85 ~ s1 + ngd1, dfO)
model10To <- lm(log10 ~ s2 + ngd2, dfO)
model50To <- lm(log10 ~ st + ngdt, dfO)
model85Ao <- lm(log85 ~ s1 + ngd1 + school85, dfO)
model10Ao <- lm(log10 ~ s2 + ngd2 + school10, dfO)
model50Ao <- lm(log10 ~ st + ngdt + school10 , dfO)
modeltest85To <- lm(log85 ~ sngd1, dfO)
modeltest10To <- lm(log10 ~ sngd2, dfO)
modeltest50To <- lm(log10 ~ sngdt, dfO)
modeltest85Ao <- lm(log85 ~ sngd1 + schoolngd1, dfO)
modeltest10Ao <- lm(log10 ~ sngd2 + schoolngd2, dfO)
modeltest50Ao <- lm(log10 ~ sngdt + schoolngdt, dfO)
```

```{r, echo = FALSE}
alphatextbook <- function(model) {
  model$coefficients[2]/(1+model$coefficients[2])
}

alphaaugment <- function(model) {
  model$coefficients[2]/(1+model$coefficients[2] + model$coefficients[3])
}

betafunc <- function(model) {
    model$coefficients[3]/(1+model$coefficients[2] + model$coefficients[3])
}
```

#Textbook Solow Model, 1960-1985
```{r, echo = FALSE}
MRWtabletextbook <- function(model1, model2, model3, model4, model5, model6) {
  a <- c(nobs(model1), nobs(model2), nobs(model3))
  b <- c(model1$coefficients[1], model2$coefficients[1], model3$coefficients[1])
  c <- c(coef(summary(model1))[1, 2], coef(summary(model2))[1, 2], coef(summary(model3))[1, 2])
  d <- c(coef(summary(model1))[1, 4], coef(summary(model2))[1, 4], coef(summary(model3))[1, 4])
  e <- c(model1$coefficients[2], model2$coefficients[2], model3$coefficients[2])
  f <- c(coef(summary(model1))[2, 2], coef(summary(model2))[2, 2], coef(summary(model3))[2, 2])
  g <- c(coef(summary(model1))[2, 4], coef(summary(model2))[2, 4], coef(summary(model3))[2, 4])
  h <- c(model1$coefficients[3], model2$coefficients[3], model3$coefficients[3])
  i <- c(coef(summary(model1))[3, 2], coef(summary(model2))[3, 2], coef(summary(model3))[3, 2])
  j <- c(coef(summary(model1))[3, 4], coef(summary(model2))[3, 4], coef(summary(model3))[3, 4])
  k <- c(summary(model1)$adj.r.squared, summary(model2)$adj.r.squared, summary(model3)$adj.r.squared)
  l <- c(summary(model1)$sigma, summary(model2)$sigma, summary(model3)$sigma)
  m <- c(NA, NA, NA)
  n <- c(model4$coefficients[1], model5$coefficients[1], model6$coefficients[1])
  o <- c(coef(summary(model4))[2], coef(summary(model5))[2], coef(summary(model6))[2])
  p <- c(coef(summary(model4))[1, 4], coef(summary(model5))[1, 4], coef(summary(model6))[1, 4])
  q <- c(model4$coefficients[2], model5$coefficients[2], model6$coefficients[2])
  r <- c(coef(summary(model4))[2, 2], coef(summary(model5))[2, 2], coef(summary(model3))[2, 2])
  s <- c(coef(summary(model4))[2, 4], coef(summary(model5))[2, 4], coef(summary(model6))[2, 4])
  t <- c(summary(model4)$adj.r.squared, summary(model5)$adj.r.squared, summary(model6)$adj.r.squared)
  u <- c(summary(model4)$sigma, summary(model5)$sigma, summary(model6)$sigma)
  v <- c(NA, NA, NA)
  w <- c(anova(model1, model4)[2,6], anova(model2, model5)[2,6], anova(model3, model6)[2,6])
  x <- c(alphatextbook(model4), alphatextbook(model5), alphatextbook(model6))
  table <- data.frame(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p, q,r,s,t,u,v, w, x)
  table[is.na(table)] = "" 
  table[1:3, 2:12] <- round(table[1:3, 2:12], 3)
  table[1:3, 14:21] <- round(table[1:3, 14:21], 3)
  table[1:3, 23:24] <- round(table[1:3, 23:24], 3)
  row.names(table) <- c("Non-Oil", "Intermediate", "OECD")
  table <- t(table)
  row.names(table) <- c("Observations", "Intercept", "se", "p", "ln(I/GDP)", "se", "p", "ln(n + g + δ)", "se", "p", "Adjusted R Squared", "see", "Restricted Regression:", "Constant", "se", "p", "ln(I/GDP) - ln(n+g+δ)", "se", "p", "Adjusted R Squared", "see", "Test of Restriction:", "p", "Implied alpha")
  print(table)
}

Table1 <- MRWtabletextbook(model85Tn, model85Ti, model85To, modeltest85Tn, modeltest85Ti, modeltest85To)
```

#Textbook Solow Model, 1985-2010
```{r, echo = FALSE}
table2 <- MRWtabletextbook(model10Tn, model10Ti, model10To, modeltest10Tn, modeltest10Ti, modeltest10To)
```
#Textbook Solow Model, 1960-2010
```{r, echo = FALSE}
table3 <- MRWtabletextbook(model50Tn, model50Ti, model50To, modeltest50Tn,modeltest50Ti, modeltest50To)
```


#Augmented Solow Model, 1960-1985
```{r, echo = FALSE}
MRWtablaugment <- function(model1, model2, model3, model4, model5, model6) {
  a <- c(nobs(model1), nobs(model2), nobs(model3))
  b <- c(model1$coefficients[1], model2$coefficients[1], model3$coefficients[1])
  c <- c(coef(summary(model1))[1, 2], coef(summary(model2))[1, 2], coef(summary(model3))[1, 2])
  d <- c(coef(summary(model1))[1, 4], coef(summary(model2))[1, 4], coef(summary(model3))[1, 4])
  e <- c(model1$coefficients[2], model2$coefficients[2], model3$coefficients[2])
  f <- c(coef(summary(model1))[2, 2], coef(summary(model2))[2, 2], coef(summary(model3))[2, 2])
  g <- c(coef(summary(model1))[2, 4], coef(summary(model2))[2, 4], coef(summary(model3))[2, 4])
  h <- c(model1$coefficients[3], model2$coefficients[3], model3$coefficients[3])
  i <- c(coef(summary(model1))[3, 2], coef(summary(model2))[3, 2], coef(summary(model3))[3, 2])
  j <- c(coef(summary(model1))[3, 4], coef(summary(model2))[3, 4], coef(summary(model3))[3, 4])
  k <- c(model1$coefficients[4], model2$coefficients[4], model3$coefficients[3])
  l <- c(coef(summary(model1))[4, 2], coef(summary(model2))[4, 2], coef(summary(model3))[4, 2])
  m <- c(coef(summary(model1))[4, 4], coef(summary(model2))[4, 4], coef(summary(model3))[4, 4])
  n <- c(summary(model1)$adj.r.squared, summary(model2)$adj.r.squared, summary(model3)$adj.r.squared)
  o <- c(summary(model1)$sigma, summary(model2)$sigma, summary(model3)$sigma)
  p <- c(NA, NA, NA)
  q <- c(model4$coefficients[1], model5$coefficients[1], model6$coefficients[1])
  r <- c(coef(summary(model4))[2], coef(summary(model5))[2], coef(summary(model6))[2])
  s <- c(coef(summary(model4))[1, 4], coef(summary(model5))[1, 4], coef(summary(model6))[1, 4])
  t <- c(model4$coefficients[2], model5$coefficients[2], model6$coefficients[2])
  u <- c(coef(summary(model4))[2, 2], coef(summary(model5))[2, 2], coef(summary(model3))[2, 2])
  v <- c(coef(summary(model4))[2, 4], coef(summary(model5))[2, 4], coef(summary(model6))[2, 4])
  w <- c(model4$coefficients[3], model5$coefficients[3], model6$coefficients[3])
  x <- c(coef(summary(model4))[3, 2], coef(summary(model5))[3, 2], coef(summary(model3))[3, 2])
  y <- c(coef(summary(model4))[3, 4], coef(summary(model5))[3, 4], coef(summary(model6))[3, 4])
  z <- c(summary(model4)$adj.r.squared, summary(model5)$adj.r.squared, summary(model6)$adj.r.squared)
  aa <- c(summary(model4)$sigma, summary(model5)$sigma, summary(model6)$sigma)
  ab <- c(NA, NA, NA)
  ac <- c(anova(model1, model4)[2,6], anova(model2, model5)[2,6], anova(model3, model6)[2,6])
  ad <- c(alphaaugment(model4), alphaaugment(model5), alphaaugment(model6))
  ae <- c(betafunc(model4), betafunc(model5), betafunc(model6))
  table <- data.frame(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p, q,r,s,t,u,v, w, x, y, z, aa, ab, ac, ad, ae)
  table[is.na(table)] = "" 
  row.names(table) <- c("Non-Oil", "Intermediate", "OECD")
  table[1:3, 2:15] <- round(table[1:3, 2:15], 2)
  table[1:3, 17:27] <- round(table[1:3, 17:27], 2)
  table[1:3, 29:31] <- round(table[1:3, 29:31], 2)
  table <- t(table)
  row.names(table) <- c("Observations", "Intercept", "se", "p", "ln(I/GDP)", "se", "p", "ln(n + g + δ)", "se", "p","ln(School)", "se", "p", "Adjusted R Squared", "s.e.e", "Restricted Regression:", "Intercept", "se", "p", "ln(I/GDP) - ln(n+g+δ)", "se", "p","ln(School) - ln(n+g+d)", "se", "p",  "Adjusted R Squared", "s.e.e", "Test of Restriction:", "p", "Implied α", "Implied b")
  print(table)
}

table4 <- MRWtablaugment(model85An, model85Ai, model85Ao, modeltest85An, modeltest85Ai, modeltest85Ao)
```

#Augmented Solow Model, 1985-2010
```{r, echo = FALSE}
table5 <- MRWtablaugment(model10An, model10Ai, model10Ao, modeltest10An, modeltest10Ai, modeltest10Ao)

```
#Augmented Solow Model, 1960-2010
```{r, echo=FALSE}
table6 <- MRWtablaugment(model50An, model50Ai, model50Ao, modeltest50An, modeltest50Ai, modeltest50Ao)


```
#Descriptive Statistics of dependent and independent variables
```{r, echo = FALSE}
stat.desc(select(dfi, c("log10", "st", "ngdt", "school10")))
```
#Summary of Augmented Model, 1960-2010, Intermediate countries
```{r, echo=FALSE}
summary(model50Ai)
```
#Ramsey Reset test
```{r, echo = FALSE}
resettest(model50Ai, 2:4)
```
#VIFs 
```{r, echo = FALSE}
vif(model50Ai)
```
#Breusch-Pagan test
```{r, echo = FALSE}
bptest(model50Ai)
```
#Summary of model with human capital replacing SCHOOL
```{r, echo= FALSE}
model50iHC <- lm(log10 ~ st + ngdt + hc_10, dfi)
model50nHC <- lm(log10 ~ st + ngdt + hc_10, dfn)
model50oHC <- lm(log10 ~ st + ngdt + hc_10, dfO)
modeltest50iHC <- lm(log10 ~ sngdt + hcngdt, dfi)
modeltest50nHC <- lm(log10 ~ sngdt + hcngdt, dfn)
modeltest50oHC <- lm(log10 ~ sngdt + hcngdt, dfO)
summary(model50iHC)
```
#Table of model with human capital index replacing SCHOOL
```{r, echo = FALSE}
MRWtablaugment(model50nHC, model50iHC, model50oHC, modeltest50nHC, modeltest50iHC, modeltest50oHC)

```
#Simple Correlation between income per capita in 2010 and human capital
```{r, echo = FALSE}
cor(dfi$hc_10, dfi$log10)
```
